Sketch of DP - Bayesian Inference

### 2018-07-14 main-sketch.tex
update section 2

We are studying the Bayesian inference in Beta-Bernoulli systems. So this part we will technically describe our problem under Beta-Bernoulli Bayesian inference systems. Suppose $\pi(\xis)$ is our prior belief about some parameters or latent variables $\xis$. By using a group of observed data $\textbf{x}$ sizing $n$, the likelihood of this group of data is $Pr(\textbf{x} | \xis)$, we produce a posterior distribution:
\begin{equation*}
Pr(\xis | \textbf{x}) = \frac{Pr(\textbf{x} | \xis) \pi(\xis)}{Pr(\textbf{x})},
\end{equation*}
denoted as $\bysinfer(\textbf{x},\pi(\xis))$ taking an observed data set $\textbf{x} \in \mathcal{X}^n$ (i.e., $\{0,1\}^n$) and a prior distribution $\pi(\xis)$ as input, outputting a posterior distribution of the parameter $\alphas$. For conciseness, when prior is given, we use $\bysinfer(x)$. $n$ is the size of the observed data size.

@@

The sensitive information we want to protect here is the posterior belief, i.e., $Pr(\xis | \textbf{x})$ rather than a sample drew from it.  we use mechanisms to protect the inference results to get private posteriors: $\dirichlet(\alphas^*)$. When we measure the distance between true posterior and protected posterior, we will have different result on $l_1$ norm and Hellinger distance. We believe that if the protected posterior is produced based on Hellinger distance, it will have a better accuracy than produced based on the $l_1$ norm.

>>>>

We are studying the Bayesian inference in Beta-Bernoulli systems. So this part we will technically describe our problem under Beta-Bernoulli systems of Bayesian inference. Suppose $\pi(\xis)$ is our prior belief about some parameters or latent variables $\xis$. By using a group of observed data $\textbf{x}$ sizing $n$, the likelihood of this group of data is $Pr(\textbf{x} | \xis)$, we produce a posterior distribution:
\begin{equation*}
Pr(\xis | \textbf{x}) = \frac{Pr(\textbf{x} | \xis) \pi(\xis)}{Pr(\textbf{x})},
\end{equation*}
denoted as $\bysinfer(\textbf{x},\pi(\xis))$ taking an observed data set $\textbf{x} \in \mathcal{X}^n$ (i.e., $\{0,1\}^n$) and a prior distribution $\pi(\xis)$ as input, outputting a posterior distribution of the parameter $\alphas$. For conciseness, when prior is given, we use $\bysinfer(x)$. $n$ is the size of the observed data size.

@@

The posterior belief about parameters $\xis$ is inferred from the group of sensitive data. Because it is usually published in form of a distribution, for example, $\betad(\alpha',\beta'), \cdots,$ themselves can relieve a lot of information about sensitive data. So, the sensitive information we want to protect here is the posterior belief, i.e., $Pr(\xis | \textbf{x})$, rather than just a sample drew from it.  we use mechanisms to protect the inference results to get private posteriors: $\dirichlet(\alphas^*)$. When we measure the distance between true posterior and protected posterior, we will have different result on $l_1$ norm and Hellinger distance. We believe that if the protected posterior is produced based on Hellinger distance, it will have a better accuracy than produced based on the $l_1$ norm.
